### 2015-02-19 paper_40_mpi.tex
working on schedule

@@

@@

                    \caption{SCHEDULE DATA NEEDED FOR MPI}
                    \label{tab:sched}
                \end{longtable}

@@

                The formula for schedule is based upon past performance.  Of the 422 projects
                scheduled since June 2013, only 45 projects had an estimated start date, estimated
                finish date and an actual finish date.  Of those 45 projects; 20 finished exactly on time,
                9 finished early and 16 finished late.

>>>>

            The MPI schedule score provides a numeric value to indicate the amount 
            schedules are missed or exceeded.  The score provides a cumulative measure
            of the performance as compared to other months.
            The score is based upon the historical deviance of estimates for
            projects.  Projects completing on time will be given a score of 0.
            Projects finishing early will be rewarded with positive scores increasing toward
            $k$. Alternatively, 
            late projects will be given negative scores that approach $-k$ as the projects
            become more late.

@@

                In order to calculate the schedule score, certain dates
                need to be present. Table \ref{tab:scheduledata} outlines
                the necessary data for schedules.  One date is considered
                optional as it is not used in the MPI calculation, but it
                is an important date that could be useful for future
                enhancements.

@@

                    \caption{SCHEDULE DATA NEEDED FOR MPI}
                    \label{tab:scheduledata}
                \end{longtable}

@@
